Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 background.tex
remove TODO in Section2.2

\textbf{Adaptive:} In this policy, the path a packet \TODO{packet granularity or message granularity?} takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths. For the non-minimal path, an intermediate router in a separate group will be randomly chosen. The packet is forwarded to the intermediate router, connecting the source and destination groups through two separate minimal paths. Adaptive routing can avoid hot-spots in the presence of congestion and collapses to minimal routing otherwise.

>>>>

\textbf{Adaptive:} In this policy, the path a packet takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths. For the non-minimal path, an intermediate router in a separate group will be randomly chosen. The packet is forwarded to the intermediate router, connecting the source and destination groups through two separate minimal paths. Adaptive routing can avoid hot-spots in the presence of congestion and collapses to minimal routing otherwise. 
%\NOTE{The Universal Globally-Adaptive Load-balanced routing (Adaptive in our paper) chooses between minimal and non-minimal on a packet by packet basis depending on the state of the network to minimize the delay of the packet~\cite{jiang}.}
